%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {General Director} % Job title
    {National Anti-corruption Secretariat} % Organization
    {Mexico City} % Location
    {Jul. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Designed the technological architecture of \href{https://www.plataformadigitalnacional.org}{Mexico's National Digital Platform} (PDN).
        The PDN is an API based web platform
        that allows interconnecting information systems with heterogeneous architectures and key anti-corruption data such as procurement, audits,
        sanctions and complaints.
        \item Led the technical team to develop data standards, synthetic data generators and web applications aimed at combating corruption.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Developer \& Technical Advisor} % Job title
    {Office of the President of Mexico, Open Government Data Section} % Organization
    {Mexico City} % Location
    {Apr. 2016 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developed several information systems and \href{https://datos.gob.mx/nuevoaeropuerto/}{data visualization web applications} to
	increase transparency and accountability of the Federal Public Administration of Mexico.
	      \item Designed and implemented an interoperability solution that allows supplying information to the \href{https://www.gob.mx/contratacionesabiertas}{Open Contracting Platform of the Federal Government of Mexico}. The interoperability solution allows the integration of data that come from the public procurement information systems of the Government of Mexico.
	      \item Participated as a technical advisor in the development of guidelines on open data. With the entry into force of the 
	      \href{http://www.dof.gob.mx/nota_detalle.php?codigo=5515623&fecha=09/03/2018}{Mexico's FinTech Law}, participated in the development of the pilot for the implementation of an \href{https://datos.gob.mx/blog/estandar-bancario-abierto-un-estandar-para-migrar-la-banca-a-la-economia-digital-del-siglo-xxi}{Open Banking Standard for Mexico}.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Chief Technology Officier} % Job title
    {Pictoline Media} % Organization
    {Mexico City} % Location
    {Mar. 2017 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Coordinated the Pictoline's  development team.
        \item Developed a web application that allowed to follow up publications on social networks and visualize its performance (reach, reactions, etc.) across time.  
        \item Collaborated in the development of a web system for publication on social networks such as Facebook, Twitter, Instagram, Tumblr, Pinterest and Imgur.
        \item Developed a web application that allowed to integrate and compare news from social networks and websites. The application was aimed at detecting common trends in different social networks.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Telecommunications Engineer} % Job title
    {Instituto Federal de Telecomunicaciones} % Organization
    {Mexico City} % Location
    {Aug. 2014 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Participated in the development of a system to measure quality in the cellular mobile service. I contributed mostly in the development of system's back-end and with a web application for results visualization. 
        \item I was appointed on several occasions as an %\href{http://www.milenio.com/firmas/fernando_mejia_barquera/Tv_Azteca-Telmex-demanda_a_Uno_Tv_18_757304308.html}{}
        expert in telecommunications engineering and computer systems.  during sanctioning processes against service providers. 
        \item Participated in the development of guidelines and technical standards in telecommunications.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {Gesfor Mexico Services} % Organization
    {Mexico City} % Location
    {Feb. 2014 - Jul. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Worked as System Administrator. Being responsible for the operation of Solaris/Linux/Windows based servers and Sybase/SQL Server databases.
        \item Developed a reporting tool using Java and SQLite (database engine).
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
